Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2020-05-11 Paper/manuscript_v2/manuscript_07_02.tex
Fix captions in fig 1&2

\begin{figure}[!t]
\centering
\subfigure{\includegraphics[scale=0.29, trim = 1mm 5mm 10mm 0mm, clip]{ch5_fig1_Post_J.pdf}}
\subfigure{\includegraphics[scale=0.29, trim = 0mm 5mm 10mm 0mm, clip]{ch5_fig1_Sigma_J.pdf}}
\subfigure{\includegraphics[scale=0.29, trim = 1mm 5mm 3mm 0mm, clip]{ch5_fig1_Cov_J.pdf}}
\vspace{-1mm}
\caption{Mean posterior predictive functions (left), covariance functions (center) and posterior standard deviations (right) of both the exact GP model (dashed red line) and the HSGP model for different number of basis functions $m$, with the boundary factor fixed to a large enough value.}
  \label{fig1_Post_J}
\end{figure}

\begin{figure}
\centering
\subfigure{\includegraphics[scale=0.29, trim = 1mm 5mm 10mm 0mm, clip]{ch5_fig2_Post_L.pdf}}
\subfigure{\includegraphics[scale=0.29, trim = 0mm 5mm 10mm 0mm, clip]{ch5_fig2_Sigma_L.pdf}}
\subfigure{\includegraphics[scale=0.29, trim = 1mm 5mm 3mm 0mm, clip]{ch5_fig2_Cov_L.pdf}}
\vspace{-1mm}
\caption{Mean posterior predictive functions (left), covariance functions (center) and posterior standard deviations (right) of both the exact GP model (dashed red line) and the HSGP model for different values of the boundary factor $c$, with a large enough fixed number of basis functions.}
  \label{fig2_Post_L}
\end{figure}

>>>>

\begin{figure}[!t]
\centering
\subfigure{\includegraphics[scale=0.29, trim = 1mm 5mm 10mm 0mm, clip]{ch5_fig1_Post_J.pdf}}
\subfigure{\includegraphics[scale=0.29, trim = 0mm 5mm 10mm 0mm, clip]{ch5_fig1_Sigma_J.pdf}}
\subfigure{\includegraphics[scale=0.29, trim = 1mm 5mm 3mm 0mm, clip]{ch5_fig1_Cov_J.pdf}}
\vspace{-1mm}
\caption{Mean posterior predictive functions (left), posterior standard deviations (center), and covariance functions (right) of both the exact GP model (dashed red line) and the HSGP model for different number of basis functions $m$, with the boundary factor fixed to a large enough value.}
  \label{fig1_Post_J}
\end{figure}

\begin{figure}
\centering
\subfigure{\includegraphics[scale=0.29, trim = 1mm 5mm 10mm 0mm, clip]{ch5_fig2_Post_L.pdf}}
\subfigure{\includegraphics[scale=0.29, trim = 0mm 5mm 10mm 0mm, clip]{ch5_fig2_Sigma_L.pdf}}
\subfigure{\includegraphics[scale=0.29, trim = 1mm 5mm 3mm 0mm, clip]{ch5_fig2_Cov_L.pdf}}
\vspace{-1mm}
\caption{Mean posterior predictive functions (left), posterior standard deviations (center), and covariance functions (right) of both the exact GP model (dashed red line) and the HSGP model for different values of the boundary factor $c$, with a large enough fixed number of basis functions.}
  \label{fig2_Post_L}
\end{figure}
